Patient-Specific Neural Field Model

### 2010-07-15 ltx/data_paper/DataPaper.tex
added cross correlation figure for determining support of kernel
minor correction to EM
added derivetive of q to the data paper

@@

 q(\mathbf x_t)=q(\hat{\mathbf x}_t)+\nabla^\top q (\hat{\mathbf x}_t)(\mathbf x_t -\hat{\mathbf x}_t)

@@

therefore

@@

 \Xi_2=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t+1}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf M_t

@@

 \Xi_3=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ]=q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t
 \Xi_4=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ]=q(\mathbf{ \hat x}_t)q^\top(\mathbf{ \hat x}_t)+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t\nabla q(\mathbf{ \hat x}_t)
we rewrite the $\mathcal Q$-function as
\begin{eqnarray}\label{eq:rewrittenQ}
 \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2  \sum_{i,j,k=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_2]_{j,k}[\boldsymbol\Sigma_e^{-1}]_{k,i} +2\xi tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
&-& \sum_{i,j,k,l=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_4]_{j,k}[ \boldsymbol\Theta^\top]_{k,l}[\boldsymbol\Sigma_e^{-1}]_{l,i} -2\xi \sum_{i,j,k=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_3]_{j,k}[\boldsymbol\Sigma_e^{-1}]_{k,i}  \nonumber \\
&-&\xi^2 tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace  
we can simplify \eqref{eq:rewrittenQ} by noting that $[\boldsymbol \Theta]_{i,j}=\mathbf 0 \quad i \neq j$

>>>>

\subsection{Estimating Support For Connectivity Kernel}
\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=-90]{./Figures/CrossCorr2D.eps}
\end{center}
\caption{{\bf Mean cross-correlations between consecutive observations of the neural field}. Note: The correlations are normalised such that the maximum value is one. A. Pre-seizure observation correlations. B. Seizure observation correlations. C. Post-seizure observation correlations.}
\label{fig:SpatialFreqObservation}
\end{figure}

@@

 q(\mathbf x_t)\approx q(\hat{\mathbf x}_t)+\nabla^\top q (\hat{\mathbf x}_t)(\mathbf x_t -\hat{\mathbf x}_t)

@@

and

@@

\frac{\delta q}{\delta x_i}= \int_\Omega \boldsymbol{\Psi}(\mathbf{r}')\phi_i(\mathbf r') f'(\phi^\top(\mathbf{r}'){x}_t) d\mathbf{r}'\\

@@

therefore
\begin{equation}
 \Xi_2=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t+1}^\top ]\approx q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t+1}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf M_t
\end{equation}
\begin{equation}
 \Xi_3=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)\mathbf x_{t}^\top ]\approx q(\mathbf{ \hat x}_t)\mathbf{ \hat x}_{t}^\top+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t
\end{equation}
\begin{equation}
 \Xi_4=\sum_{t=1}^{T}\mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ], \quad \mathbf E_{(\theta',\xi')}[q(\mathbf x_t)q^\top(\mathbf x_t) ] \approx q(\mathbf{ \hat x}_t)q^\top(\mathbf{ \hat x}_t)+\nabla^\top q(\mathbf{ \hat x}_t)\mathbf P_t\nabla q(\mathbf{ \hat x}_t)
\end{equation}
we rewrite the $\mathcal Q$-function as
\begin{eqnarray}\label{eq:rewrittenQ}
 \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=&\beta+2  \sum_{i,j,k=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_2]_{j,k}[\boldsymbol\Sigma_e^{-1}]_{k,i} +2\xi tr \left\lbrace  \Xi_0\boldsymbol\Sigma_e^{-1}\right\rbrace  \nonumber \\
&-& \sum_{i,j,k,l=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_4]_{j,k}[ \boldsymbol\Theta^\top]_{k,l}[\boldsymbol\Sigma_e^{-1}]_{l,i} -2\xi \sum_{i,j,k=1}^{n_x}[\boldsymbol\Theta]_{i,j}[\Xi_3]_{j,k}[\boldsymbol\Sigma_e^{-1}]_{k,i}  \nonumber \\
&-&\xi^2 tr \left\lbrace \Xi_1\boldsymbol\Sigma_e^{-1}\right\rbrace  
\end{eqnarray}
we can simplify \eqref{eq:rewrittenQ} by noting that $[\boldsymbol \Theta]_{i,j}=\mathbf 0 \quad i \neq j$
